Pipeline systems and infrastructure for the efficient and open processing of Big neuroimaging Data

### 2018-10-01 paper.tex
some text on portability

                Writting BigData to Lustre is very costly compared to local 
                node storage. BigData filesystems like HDFS may not necessarily
                be the best solution for HPC as they will not only use up 
                storage on compute nodes, but also replicate the data across 
                the cluster taking up a significant amount of storage space.
                Moreover, while BigData frameworks typically execute on a 
                dedicated BigData cluster, they will be on a shared cluster in
                HPC, with many processed trying to access the memory. The 
                following are two optimizations made for

                Alluxio, formerly known as Tachyon, is an in-memory filesystem
                that stores lineage data to offset the cost of writing data to 
                disk. The assumption that Alluxio makes is that it will be less
                costly to recompute the data that to store the data to disk and
                replicate across the network for fault tolerance. However,
                unlike Spark applications, Alluxio is meant to run indefinitely
                , making it unfavourable, in some cases, to recompute the data
                from its starting point. For this, Alluxio evaluates the 
                lineage data and selects

                Triple-H leverages the heterogeneity of HPC clusters to 
                optimize the data's placement across the cluster for most 
                efficient use.

@@

            dask distributed
            \note{scientific: SLURM, PBS, SGE, HTCondor, Mesos (sometimes)
            big data: mapreduce - local or YARN, Spark - standalone, YARN or 
            Mesos, dask: any (easy to extend to any scheduler)}
        \section{Performance enhancement strategies}\label{other}
            scientific: workflow checkpointing (looking at file hashes)
            big data: data locality, in memory computing, lazy evaluation
    \chapter{Portability}\label{portability}
        java or python backend (most) typically platform independent (some 
        exceptions)
        all tools used in the pipeline must be installed on system
        Taverna - exception as relies on web services
        \section{Containers}

>>>>

                Writting BigData to Lustre is very costly compared to local 
                node storage. BigData filesystems like HDFS may not necessarily
                be the best solution for HPC as they will not only use up 
                storage on compute nodes, but also replicate the data across 
                the cluster taking up a significant amount of storage space.
                Moreover, while BigData frameworks typically execute on a 
                dedicated BigData cluster, they will be on a shared cluster in
                HPC, with many processed trying to access the memory. The 
                following are two optimizations made for  \note{two or one}

                Alluxio, formerly known as Tachyon, is an in-memory filesystem
                that stores lineage data to offset the cost of writing data to 
                disk. The assumption that Alluxio makes is that it will be less
                costly to recompute the data that to store the data to disk and
                replicate across the network for fault tolerance. However,
                unlike Spark applications, Alluxio is meant to run indefinitely
                , making it unfavourable, in some cases, to recompute the data
                from its starting point. For this, Alluxio evaluates the 
                lineage data and selects the

                Triple-H leverages the heterogeneity of HPC clusters to 
                optimize the data's placement across the cluster for most 
                efficient use. It has two modes, default and Lustre integrated,
                that allows it to execute on systems with and without access
                to a distributed filesystem.

@@

            dask distributed
            \note{scientific: SLURM, PBS, SGE, HTCondor, Mesos (sometimes)
            big data: mapreduce - local or YARN, Spark - standalone, YARN or 
            Mesos, dask: any (easy to extend to any scheduler)}
        \section{Performance enhancement strategies}\label{other}
            scientific: workflow checkpointing (looking at file hashes)
            big data: data locality, in memory computing, lazy evaluation
    \chapter{Portability}\label{portability}
        In order for a workflow engine to be utilized, it much be simple for 
        users to install and execute the data. Platform-independence of both 
        the frameworks and tools, as well as, simple installation of all 
        necessary components and straightforward execution of workflows  are a 
        requirement for frameworks and their respective pipelines to be 
        portable. Without portability, users are limited to executing certain
        frameworks only or dealing with the significant overhead of making 
        these engines work on the system available to them. In this chapter, 
        we evaluate the portability of workflows on the basis of the following
        three components: 1) platform-independence, 2) tool installation and
        3) execution setup. We also examine containerization, one of the 
        strategies used to improve portability.

        \section{Platform-independence}
            Achieving platform-independence allows users to use the workflow 
            engine in any available environment. This however does not imply 
            that the tools, and as a consequence, the pipelines created will
            also be platform-independent. Many workflow engines have opted to 
            be platform independent. These workflow engines include: Nipype,
            PSOM, SPM, FASTR, LONI, AA, Pydpiper, Taverna, MapReduce, Spark and
            Dask. These workflow engines achieve platform independence through
            running on the Java Virtual Machine (JVM) or being written in 
            Python. Platform-independent engines that are Java-based include: 
            PSOM, SPM, LONI, AA, Taverna, MapReduce and Spark. The remainder of
            the pipelines are implemented in Python. The remainder of the 
            workflow engines (Pegasus, Make, OpenMOLE, Nextflow, Galaxy, and 
            Toil are not platform-independent, but can execute on UNIX-like 
            systems.

            Engines built ontop of a platform-independent language does not 
            necessarily imply platform independence. For instance, OpenMOLE is 
            built in Scala and Netflow runs on Groovy, yet neither are platform
            independent. In the case of OpenMOLE, this is due to its CARETask
            blackbox, which is only possible for Linux environments. However,
            many tools and programs available for incorporation into workflows
            are platform-dependent. For example, even though Nipype is 
            platform-independent, common tools used in Nipype modules, such as 
            FreeSurfer and FSL, are Linux-based. Moreover, HPC infrastructure 
            is usually Linux-based and it is therefore crucial that all 
            workflows are compatible with and tested on Linux systems.

       \section{Tool installation}

            Unless a user is building a workflow exclusively based on custom
            functions or using a monolithic workflow engine such as SPM, they
            will need to install the tools necessary for their workflow on
            their computer or cluster. Depending on the workflow engine 
            selected, this may be managed by the engine, or the user may be 
            left to install the dependencies themselves. Workflow engines that
            delegate tool installation to the user include: Nipype, PSOM,

        Many of these platforms have selected to be written in 
        platform-independent languages. However,  Due to the modularity of these
        frameworks, it may be necessary
        java or python backend (most) typically platform independent (some 
        exceptions)
        all tools used in the pipeline must be installed on system
        Taverna - exception as relies on web services
        \section{Containers}
